---
title: "Time Series Analysis-Regression Models Template"
author: "Muuzaani Nkhoma"
date: "May 28, 2018"
output: html_document
---

```{r setup, include=FALSE}

### Load Packages run once before running the program or as needed
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(MASS)
library(tidyverse)
library(forecast)
library(plotly) # For trellises

```


##### Read, Explore, and Prepare the data

```{r }

print("Start importing dataset")
fatal <- read_csv("Data Time Series/Table B.25 U.S.Traffic Fatalities.csv")

dim(fatal)
ncol(fatal)
nrow(fatal)
names(fatal)
print("Finished importing dataset")

```


```{r}

fatal.ts <- as.ts(fatal)

```

##### View first observations

```{r }

head(fatal.ts)

```

##### View last observations
```{r }

tail(fatal.ts)

```

##### Summary Statistics

```{r }

summary(fatal.ts)

```

##### Plot Scatterplots
To investigate the linear relationship between response and 
regressor variables

```{r}

pairs(fatal.ts)

```


######Correlation Matrix
Test for correlation to get the values of the correlation between response and regressor variables

```{r }

cor(fatal.ts)

```


```{r}

fatal.ts %>%
  as.data.frame() %>%
  GGally::ggpairs()
```


```{r}
autoplot(fatal.ts[,c("ResPopul", "LicDriv", "RegMV", "MVMiles", "AnnUR")]) +
  ylab("Variables") + xlab("Year")

```


```{r}
vars <- setdiff(names(fatal), "Year")
plots <- lapply(vars, function(var) {
  plot_ly(fatal, x = ~Year, y = as.formula(paste0("~", var))) %>%
    add_lines(name = var)
})
subplot(plots, nrows = length(plots), shareX = TRUE, titleX = FALSE)
```


#####Fit the Full model with all regressor variables

```{r }

print("Started fitting the linear model")
fatal.model <- tslm(Fatal ~ ResPopul + LicDriv + RegMV + MVMiles + AnnUR, data = fatal.ts) 
print("Finished fitting linear model")

```

##### Summary Statistics

```{r }

summary.lm(fatal.model)

```

##### ANOVA TABLE

```{r }

 anova(fatal.model)

```


```{r }

print("Start fitting predicted and residual values")
fatal.model.fit = fitted(fatal.model)
fatal.model.res = residuals(fatal.model)
fatal.model.stdres= rstudent(fatal.model)
print("Finished fitting predicted and residual values")

```


##### Calculate the predictive residuals in the Full Model


```{r }

AIC(fatal.model)

```

```{r }

BIC(fatal.model)

```

#####Press Statistic
```{r }

pr <- residuals(fatal.model)/(1-lm.influence(fatal.model)$hat)
#' calculate the PRESS
PRESS <- sum(pr^2)
PRESS

```


#####Checking multicollinearity for independent variables in the Full Model.


```{r }

library(perturb)
car::vif(fatal.model)

```


```{r }

car::vif(fatal.model) > 10 #Cutoff Point

```




#####Eigensystem Analysis
Condition Number          < 100: No serious problem
100<= condition number < 1000: Moderate to strong multicollinerity
Condition Number       >= 1000: Severe multicollinearity

At least one condition Index >= 1000 means near linear dependency

```{r }

print(colldiag(fatal.model))

```


#### Full Model Diagnostics

(Are all the conditions satisfied? LINE)
(What regressors seem important?)
(Any Possible Outliers?)
(Is there any need for transformation of response or regressor variables?)

####Residual Analysis
#####Diagnostics Plot

```{r }

checkresiduals(fatal.model)


```



```{r}
fatal.model.fit = fitted(fatal.model)
fatal.model.res=residuals(fatal.model)

cbind(fatal.model.fit = fitted(fatal.model), 
      fatal.model.res=residuals(fatal.model)) %>%
  as.data.frame() %>%
  ggplot(aes(x=Fitted, y=Residuals)) + geom_point()

```


####MODEL ADEQUACY CHECKING

####Model Diagnostics
####Residual Analysis

#####Diagnostics Plots- Normal Probability and Histogram
Check for Residual Normality
Check for Outliers

```{r }

par(mfrow=c(1,2),oma=c(0,0,0,0))
qqnorm(fatal.model.res,pch=16)
qqline(fatal.model.res, col = 2)
hist(fatal.model.res, col="gray",xlab='Residual',main='Histogram of Studentized \nResiduals Model #1')

```

#### Model Diagnostics
####Residual Analysis

####Diagnostics Plot- Studentized Residuals and R-Student Residual Plots

Check for Equal(Constant) Variance
Check for Outliers
Check for nonlinearity or other Patterns

```{r }

par(mfrow=c(1,2),oma=c(0,0,0,0))
plot(fatal.model.res~fatal.model.fit,pch=16,xlab='Fitted Value',ylab='studentized Residuals', 
     main = "Studentized Residuals \nvs Fits Model #1")
abline(h = 0)
plot(fatal.model.stdres~fatal.model.fit,pch=16,xlab='Fitted Value',ylab='R-Student Residuals', 
     main = "R-Student Residuals \nvs Fits Model #1")
abline(h = 0)

```

##### Model and Variable Selection
(To be performed if the number of variables is very large)
(Otherwise go straight to All Possible Regression )

##### Stepwise Regression Model Selection

```{r }

step(lm(Fatal~.-Year, data = fatal),direction="both")

```

##### Backward Regression Model Selection

```{r }

step(lm(Fatal~.-Year, data = fatal),direction="backward")

```

#####Forward Regression Model Selection

```{r }

step(lm(Fatal~.-Year, data = fatal),direction="forward")

```


#####  Evaluate Subset Regression Models
#####   All Subsets Regression

```{r }

library(leaps)
attach(fatal)
fatal.regsubsets <-regsubsets(Fatal~.-Year, data = fatal,nbest=5)
fatal.regsubsets.summary   =summary(fatal.regsubsets,all.best=TRUE,matrix=TRUE,matrix.logical=FALSE,df=NULL)

names(fatal.regsubsets.summary)


```


```{r }

fatal.regsubsets.summary$outmat

```


```{r }

layout(matrix(1:1, ncol = 2))
## Mallow Cp
res.legend <- subsets(fatal.regsubsets, statistic="cp", legend = FALSE, min.size = 1, main = "Mallow Cp")
abline(a = 1, b = 1, lty = 2)

```


```{r }

layout(matrix(1:1, ncol = 2))
## Adjusted R2
res.legend <- subsets(fatal.regsubsets, statistic="adjr2", legend = FALSE, min.size = 1, main = "Adjusted R^2")
abline(a = 1, b = 1, lty = 2)

```

```{r }

plot(fatal.regsubsets,scale="Cp")

```

```{r }

fatal.regsubsets.summary$cp

```

```{r }

plot(fatal.regsubsets,scale="adjr2")

```

```{r }

fatal.regsubsets.summary$adjr2

```

```{r }

fatal.regsubsets.summary$outmat[8, ]
fatal.regsubsets.summary$outmat[16, ]
                
```


```{r }

fatal.regsubsets.summary$cp[8]
fatal.regsubsets.summary$cp[16]
                
```


```{r }

fatal.regsubsets.summary$adjr2[8]
fatal.regsubsets.summary$adjr2[16]
                
```


```{r }

fatal.regsubsets.summary$rss[8]
fatal.regsubsets.summary$rss[16]
                
```

```{r }

fatal.regsubsets.summary$bic[8]
fatal.regsubsets.summary$bic[16]

```

```{r }

fatal.regsubsets.summary$rsq[8]
fatal.regsubsets.summary$rsq[16]

```

#### Analysis of Individual Chosen Models


##### Chosen Models:

```{r }
#1 From Scatterplots
lm(formula = Fatal ~  AnnUR , data = fatal)
#2 From All Possible Regression
lm(formula = Fatal ~ RegMV + AnnUR, data = fatal)
#3 From Stepwise Selection Process
lm(formula = Fatal ~ ResPopul + AnnUR, data = fatal)
#4 From Backward Selection Process
lm(formula = Fatal ~ ResPopul + AnnUR, data = fatal)
#5 From Forward Selection Process
lm(formula = Fatal ~ (Year +ResPopul + LicDriv + RegMV  + 
    MVMiles + AnnUR) - Year, data = fatal)


```

#### Candidate Model #1
 fatalities ~ motorvehicles + unemployment

##### Fitting the model


```{r }

fatal.model <- lm(formula = Fatal ~ RegMV + AnnUR, data = fatal) 

```

##### Model Summary

```{r }

summary.lm(fatal.model)

```

##### Model Analysis of Variance 

```{r }

anova(fatal.model)

```

#####Fitted and Residual Values

```{r }
  
fatal.model.fit = Fitted
fatal.model.res = Residuals
#fatal.model.stdres= rstudent(fatal.model)

```

####MODEL ADEQUACY CHECKING

####Model Diagnostics
####Residual Analysis

#####Diagnostics Plots- Normal Probability and Histogram
Check for Residual Normality
Check for Outliers

```{r }

par(mfrow=c(1,2),oma=c(0,0,0,0))
qqnorm(fatal.model.res,pch=16)
qqline(fatal.model.res, col = 2)
hist(fatal.model.res, col="gray",xlab='Residual',main='Histogram of Studentized \nResiduals Model #1')

```

#### Model Diagnostics
####Residual Analysis

####Diagnostics Plot- Studentized Residuals and R-Student Residual Plots

Check for Equal(Constant) Variance
Check for Outliers
Check for nonlinearity or other Patterns

```{r }

par(mfrow=c(1,2),oma=c(0,0,0,0))
plot(fatal.model.res~fatal.model.fit,pch=16,xlab='Fitted Value',ylab='studentized Residuals', 
     main = "Studentized Residuals \nvs Fits Model #1")
abline(h = 0)
plot(fatal.model.stdres~fatal.model.fit,pch=16,xlab='Fitted Value',ylab='R-Student Residuals', 
     main = "R-Student Residuals \nvs Fits Model #1")
abline(h = 0)

```

#####Further Residual Analysis
#####Partial Regression Plots

Assess linearity of individual regressors
Check for added- Value/Marginal usefulenes of regressor variables


```{r, eval=FALSE}

#Partial Regression Plots Model #1
par(mfrow=c(1,2),oma=c(0,0,0,0))
# Regress y on other regressors without candidate regressor
fatal.model.x2 <- lm(formula = y ~ x3, data = fatal)
fatal.model.x3 <- lm(formula = y ~ x2 , data = fatal)
# Regress candidate regressor on other remaining regressors
model.x2 <- lm(x2 ~ x3, data = fatal)
model.x3 <- lm(x3 ~ x2, data = fatal)

```

#####Partial Regression Plots Model #1

```{r,eval=FALSE }

plot(resid(fatal.model.x2)~resid(model.x2), pch=16,
     xlab = "residuals of x2 vs other x",
     ylab = "residuals of y vs other x",
     main = "Partial Regression \nPlot of \nModel #1 x2")
abline(lm(resid(fatal.model.x2)~resid(model.x2)))

plot(resid(fatal.model.x3)~resid(model.x3), pch=16,
     xlab = "residuals of x3 vs other x",
     ylab = "residuals of y vs other x",
     main = "Partial Regression \nPlot of \nModel #1 x3")
abline(lm(resid(fatal.model.x3)~resid(model.x3)))

```

####Model Diagnostics
#####Lack-of-fit test

```{r,eval=FALSE }

library(alr3)
pureErrorAnova(fatal.model)

```

```{r,eval=FALSE }

Reduced=fatal.model #fit reduced model
Full=lm(Fatal ~  0 + as.factor(RegMV) + as.factor(AnnUR), data = fatal) #fit full model
anova(Reduced, Full) #get lack-of-fit test

``` 

####TRANSFORMATIONS AND POLYNOMIAL REGRESSION
Dealing with Constant Variance and Non-Normality
####a.Linear Transformation

#####Box-Cox Method Transformation on y 

#####Box- Cox Method
```{r,eval=FALSE }

boxcox(Fatal ~ ., data = fatal,
       lambda = seq(-1.5, 1.5, length = 10))

```

#####b. Weighted Least Squares
Define the weights and fit the model:
Response yi1

```{r,eval=FALSE }
#Needs a standard deviation column created from local means
y1respw.model = lm(yi1~x1 + x2 + x3, weights = SD, data = taguchidf)
summary(y1respw.model)

```

Try fitting the regression without weights and see what the difference is.

```{r,eval=FALSE }
gu <- lm(crossx ~ energy, strongx)
summary(gu)

```

The two fits can be compared
```{r,eval=FALSE}
plot(crossx ~ energy, data=strongx)
 abline(g)
 abline(gu,lty=2)
 
```

####Polynomial Regression
#####Dealing with nonlinear or curvelinesr problems


####DIAGNOSTICS-LEVERAGE AND INFLUENTIAL ANALYSIS

####SUMMARY

#####Influence

```{r }

fatal.model.infl <- influence.measures(fatal.model)
p1 = 2                #Number of regressor variables under consideration
p1
n1 = 47     #Number of Observations
n1
#Influential Diagnostics Summary
summary(fatal.model.infl) # only these

```

####Model Diagnostics
####Influential Analysis

#####1 DFFITS 
(how much the regression function changes at the i-th case / 
observation when the  i -th case / observation is deleted.)
identify DFFITS values > 2/(sqrt(nrow(fatald))

```{r }

cutoffdf1 =  2 /sqrt(p1/n1) 
cutoffdf1
fatal.model.dfits = dffits(fatal.model)
plot(dffits(fatal.model), pch=16, ylab="DFFITS", main = "DFFITS Plot of Model #1")
abline(h = cutoffdf1)

```

####Model Diagnostics
#####Influential Analysis

#2 Cook's D  (how much the entire regression function changes when 
# the i -th case is deleted)
# identify D values > 4/(n-p-1) 

```{r }

cutoffCD1 =  4/(n1-p1-1) 
cutoffCD1
plot(cooks.distance(fatal.model), pch=20,  ylab="Cook's distance", main = "Cook's Distance\n  Plot of Model #1")
abline(h = cutoffCD1)

```

####Model Diagnostics
##Influential Analysis

#3 DFBETAS plot (measures how much the coefficients change when the i-th case is deleted.)
# identify DFBETAS values > 2/(sqrt(nrow(fatald))

```{r }

cutoffdb1 = 2 / sqrt(n1)
cutoffdb1
fatal.model.dfb = dfbeta(fatal.model, infl = lm.influence(fatal.model, do.coef = TRUE))
plot(dfbetas(fatal.model), pch=20, ylab="DBETAS", main = "DFBETAS Plot of Model #1")

```

####Model Diagnostics
####Influential Analysis

#####4 Leverage Points 
(regressor variable with the largest distance from the center of the centroid)
which observations 'are' influential X-Value Outliers
(2 * p) / n

```{r }

cutoffhat1 = (2 * p1) / n1
cutoffhat1
plot(hatvalues(fatal.model), pch=20, ylab='Hat values', main = "Levereage Points Plot\n of Model #1")
abline(h = cutoffhat1)

```

####Model Diagnostics
#####Influential Analysis

##### OtherPlots of Influence

```{r,eval=FALSE }

plot(rstudent(fatal.model) ~ hatvalues(fatal.model),pch=20, main = "R-Student Residuals \nvs Leverage Model #3") # recommended by some
plot(fatal.model,pch=20, which = 5) # an enhanced version of that via plot(<lm>)
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fatal.model)

```
####Model Diagnostics

#####Influential Diagnostics Output

```{r,eval=FALSE }

fatal.model.infl <- influence.measures(fatal.model)
fatal.model.infl         # all

```

#### MULTICOLLINEARITY DIAGNOSTICS

Checking multicollinearity for independent variables.
Check for extent of lack of orthogonality and sources

#####1.Variance Inflation Factors

```{r }

car::vif(fatal.model) # variance inflation factors 
car::vif(fatal.model) > 10 # problem?

```

####2.Eigensystem Analysis
Condition Number          < 100: No serious problem
100<= condition number < 1000: Moderate to strong multicollinerity
Condition Number       >= 1000: Severe multicollinearity

Condition Index > 30 and variance decomposition proportion 0.5 means near linear dependency and indicates multicollinearity

#####a.Variance Decomposition Proportions

```{r }

print(colldiag(fatal.model))

```

#####b.Variance Decomposition Proportions (Centered)

```{r }

print(colldiag(fatal.model), center = TRUE)

```

####DETECTING AUTOCORRELATION:THE DURBIN-WATSON TEST 


##### Load Orcutt package
```{r }

library(orcutt)

```

#### DURBIN_WATSON TEST
Decision Procedure
If d < dL reject H0 : phi  = 0???
If d > dU do not reject H0 : phi = 0??? = 
If dL ???d???dU the test is inconclusive where d is the DW statistic

##### Run the test
```{r }

dwt(fatal.model, alternative="positive")

```

##### Residuals versus Time Plot

```{r }

par(mfrow=c(1,1),oma=c(0,0,0,0))
plot(fatal.model.res~fatal$Year,pch=16,xlab='Year',ylab='Residuals', 
     main = "Residuals vs Time Plot \nfor Model #1")


```


##### Estimate the parameter estimates using cochran.orcutt function.

```{r }

fatal.model.cofit<-cochrane.orcutt(fatal.model)
fatal.model.cofit

```

# Summary of the transformed model without autocorrelation.

```{r 1c}

summary(fatal.model.cofit)

```



#### 9.REGRESSION MODELS WITH ARIMA ERRORS



##### Read, Explore, and Prepare the data

```{r }

print("Start importing dataset")

load(file = "Data/soybeanImputed.Rda")


dim(soybeanImputed)
ncol(soybeanImputed)
nrow(soybeanImputed)
names(soybeanImputed)
print("Finished importing dataset")

```


##### View first observations

```{r }

head(soybeanImputed)

```

##### View last observations
```{r }

tail(soybeanImputed)

```

##### Summary Statistics

```{r }

summary(soybeanImputed)

```




##### Split data

```{r}

soybeanImputed.train <- soybeanImputed[1:452, ]

dim(soybeanImputed.train)

#soybeanImputed.test <- soybeanImputed[401:517,  ]

#dim(soybeanImputed.test)

```




### Missing Values

```{r}

plot_missing(soybeanImputed.train)

```


```{r}

Mar2020.regArima.train <- soybeanImputed.train

dim(Mar2020.regArima.train)

plot_missing(Mar2020.regArima.train)


```


```{r, eval = FALSE, include = FALSE}

regressors.ts <- Mar2020.regArima.train %>%
  select(MarClose, MayClose, JulyClose, SM_TIn, SO_Ostk, SO_TIn, SO_Tout, Soybean_Meal)

regressors.ts <- as.data.frame(regressors.ts)

autoplot(regressors.ts[, c(MarClose, MayClose, JulyClose, SM_TIn, SO_Ostk, SO_TIn, SO_Tout, Soybean_Meal)], main = "Soybean Variables", facets = TRUE, xlab = "Month",
  ylab = "1000 short tons") 

```





#####Fit the Full model with all regressor variables


```{r }

print("Started fitting the linear model")

Mar2020.regressors.train <- cbind(Mar2020.regArima.train$SM_TIn, Mar2020.regArima.train$SO_Ostk, Mar2020.regArima.train$SO_TIn, Mar2020.regArima.train$SO_Tout, Mar2020.regArima.train$Soybean_Meal)

Mar2020.regArima.trainModel <- auto.arima(Mar2020.regArima.train$MarClose,
  xreg = Mar2020.regressors.train, stepwise = TRUE)
print("Finished fitting linear model")

```



```{r}
Mar2020.regre.ts <- ts(Mar2020.regArima.train, frequency = 7)
plot(decompose(Mar2020.regre.ts[ ,6]))

```


```{r}
Mar2020.regre.ts <- ts(Mar2020.regArima.train, frequency = 7)
plot(decompose(Mar2020.regre.ts[ ,8]))

```


```{r}
Mar2020.regre.ts <- ts(Mar2020.regArima.train, frequency = 7)
plot(decompose(Mar2020.regre.ts[ ,11]))

```


```{r}
Mar2020.regre.ts <- ts(Mar2020.regArima.train, frequency = 7)
plot(decompose(Mar2020.regre.ts[ ,15]))

```


```{r}
Mar2020.regre.ts <- ts(Mar2020.regArima.train, frequency = 7)
plot(decompose(Mar2020.regre.ts[ ,18]))

```


Model Summary

```{r}

summary(Mar2020.regArima.trainModel)

```

# (yt = 946.3165 - 0.0067xreg1 - 0.0161xreg2 + 0.0149xreg3 - 0.0049xreg4 + 0.0541xreg5 + 0.3761yt-1 + 0.5957yt-2 - 0.5305errort-1)


#### Full Model Diagnostics

(Are all the conditions satisfied? LINE)
(What regressors seem important?)
(Any Possible Outliers?)
(Is there any need for transformation of response or regressor variables?)

####Residual Analysis
#####Diagnostics Plot

```{r }

checkresiduals(Mar2020.regArima.trainModel)


```



#### Test for seasonality in the time series

```{r}

plot(decompose(March2020.ts))

```

```{r, eval = FALSE, include = FALSE}
#Creating  important variables csv file

#regressorIndValues <- soybeanImputed[453:517, ]

#write.table(regressorIndValues, "Data/regressorIndValues.csv", sep = ",", row.names = F) # save as a .csv file


```


```{r, include = FALSE}

SM_Prod <- c(3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 3997.429, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4003.248, 4007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 40007.903, 4007.903)

SM_TIn <- c(4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4439.874, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4444.041, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374, 
4447.374
)

SM_Dom <- c(3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3106.54,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3127.105,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558,
3143.558
)

SO_Ostk <- c(1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1794.574,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1675.494,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983,
1617.983
)

SO_Prod <- c(1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1973.078,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1975.973,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289,
1978.289
)

SO_Imp <- c(33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.46121,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.72314,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506,
33.98506
)

SO_TIn <- c(3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3985.837,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3949.03,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223,
3912.223
)

SO_Dom <- c(2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2088.585,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2119.229,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77,
2143.77
)

SO_Biodiesel <- c(723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
723.5234,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
732.4518,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944,
739.5944
)

SO_Exp <- c(121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
121.86699,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
110.30848,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997,
98.74997
)

SO_Tout <- c(2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2163.514,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2181.149,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256,
2195.256
)

SO_CStk <- c(1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1645.601,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1597.312,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078,
1642.078
)

VoFP_Flaxseed <- c(8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.84,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.692459,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946,
8.524946
)

Soybean_Meal <- c(295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.57,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
295.9191,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786,
293.786
)

ImCon_Oriented <- c(118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6152,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266,
118.6266
)

#Mar2020.forecast.regressors <- cbind(SM_Prod, SM_TIn, SM_Dom, SO_Ostk, SO_Prod,  SO_TIn, SO_Dom, SO_Biodiesel, SO_Exp, SO_Tout, SO_CStk, Soybean_Meal)



forecast.regressors <- cbind(SM_TIn, SO_Ostk,  SO_TIn, SO_Tout, Soybean_Meal)


#2 Claude
#forecast.regressors <- cbind(SM_Prod, SM_TIn, SM_Dom, SO_Ostk, SO_Prod, SO_Imp, SO_Dom, SO_Biodiesel, SO_Exp, VoFP_Flaxseed, Soybean_Meal)


#cbind(Mar2020.regArima.train$SM_TIn, Mar2020.regArima.train$SO_Ostk, Mar2020.regArima.train$SO_TIn, Mar2020.regArima.train$SO_Tout, Mar2020.regArima.train$Soybean_Meal)


#cbind(Mar2020.regArima.train$SM_Prod, Mar2020.regArima.train$SM_TIn, Mar2020.regArima.train$SM_Dom, Mar2020.regArima.train$SO_Ostk, Mar2020.regArima.train$SO_Prod, Mar2020.regArima.train$SO_TIn, Mar2020.regArima.train$SO_Dom, Mar2020.regArima.train$SO_Biodiesel, Mar2020.regArima.train$SO_Exp, Mar2020.regArima.train$SO_Tout, Mar2020.regArima.train$SO_CStk,   Mar2020.regArima.train$Soybean_Meal)

```


#### Test for seasonality in the time series

```{r}

plot(decompose(March2020.ts))

```

####Forecasting


#####d. one-step-ahead forecasts for (60 days): September 1, 2019 - November 10, 2019

```{r}


Mar2020.regArima.test.fore <- forecast(Mar2020.regArima.trainModel,xreg = forecast.regressors)

autoplot(Mar2020.regArima.test.fore) + xlab("Day") +
  ylab("March 2020 CONTRACT PRICE")

```


####Foreacsting


#####d. one-step-ahead forecasts for (60 days): September 1, 2019 - November 10, 2019

```{r}

Mar2020.regArima.test.fore <- forecast(Mar2020.regArima.trainModel, xreg = forecast.regressors, h = 52)

autoplot(Mar2020.regArima.test.fore) + xlab("Day") +
  ylab("March 2020 Contract Prices")

```


#####e. Model Performance
#####checks accuracy of forecast model
##### Forecast accuracy measures on the log scale.

##### in-sample one-step forecasts.

```{r, eval = FALSE}

Mar2020.regArima.trainModel.ac <- accuracy(Mar2020.regArima.trainModel.fore)
Mar2020.regArima.trainModel.ac

```




##### out-of-sample one-step forecasts.

```{r}

Mar2020.regArima.fore.ac<-accuracy(Mar2020.regArima.test.fore)
Mar2020.regArima.fore.ac

```



##### REtrieving the errors

```{r}

reg_error = residuals(Mar2020.regArima.trainModel, type="regression")
arima_error = residuals(Mar2020.regArima.trainModel, type="innovation")

```
